---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# mlbgm

<!-- badges: start -->
<!-- badges: end -->

The goal of `mlbgm` is to streamline access to data that answers questions that Major League Baseball executives care about. These include:

- How good was/is/will be that player? 
    - Player evaluation (past performance)
    - Player projection (future performance)
- How good was/is/will be that team? 
    - Team evalation and projection
- How much will that player cost? 
    - Salaries (past and future)
    - Major League Serice
- How much money are we making? 
    - Franchise valuation and revenue

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("beanumber/mlbgm")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(mlbgm)
lkup_teams()
lkup_players
```

# References

`mlbgm` works in conjunctions with other tools, including:

- [Lahman](https://github.com/cdalzell/Lahman)
- [teamcolors](https://www.github.com/beanumber/teamcolors)
- [baseballr](http://www.github.com/BillPetti/baseballr)
- [statcastr](http://www.github.com/beanumber/statcastr)
- [retro](http://www.github.com/beanumber/retro)


